How to Find GENERAL Defect Prediction Models \\ Amidst Hundreds of Software Projects

### 2020-03-12 response.tex

\response{
Over-fitting is a problem that can occur with data of any size. Over-fitting is a well-studies problem that explores bias/variance trade offs.
But over-fitting is an orthogonal issue to Transfer learning.
To clarify all that we have added text to XXX:}
\begin{quote}
\response{
\respto{2-XXX}
This sections ask if conclusions always improve as we learn from more and more data.
This can be an issue since if a new project
is fundamentally different to all past projects, then irrelevant ideas from the past will be
inappropriately applied to the present situation. ~\\
is a special problem that arises when combining old data/models with new data/models.}
\end{quote}

\review{(2.22) [Abstract] “When one exemplar project…offers the best advice then it can be used to offer advice for many other projects.” The word advice is confusing here. The so-called bellwether does not offer advice or recommendations. It is simply used as a characterization, right?}

\response{Thank you for your comment, you are quite correct the use of ``advice or recommendations'' is rather ambiguous in this context. We have changed these references of ``advice or recommendations'' to ``prediction'' in this version of manuscript }

\review{(2.23) [Sec. 2.3] “…among developers, there is little agreement on what many issues relating to software.” Please reword.}

\response{Thank you for your comment. We have made changes \respto{2-23} to the sentence to be understandable }

\review{(2.24) [Sec. 2.3(c)] “For example…” is a run-on sentence.}

\response{Thank you for your comments, we have rechecked the manuscript for such run-on-sentences and fixed them in this version.}

\review{(2.25) [Sec. 3] What are the units for dataset size in Fig. 4?}

\response{Thank you for your comment, we forgot to include the unit for dataset size in Fig. 4 (Now Fig~\ref{fig:meta}) in the last  version. The unit for dataset size is number of rows for each dataset and it has been added into the figure as well.}

\review{(2.26) [Sec. 5] Why do you need a figure (Fig. 6) for two numbers?}

\response{Thank you for your comment, the figure Fig. 6 (now Fig~\ref{fig:time}) is important as this figure shows the difference of time taken for each method. XXXXXXX include with updated charts.XXXXXXX}

@@

\section*{Reviewer 3}

\review{(3.1)What I find irritating is that the manuscript introduces a new approach GENERAL, which just applies hierarchical clustering. As far as I understand, hierarchical clustering is a well-known, standard, and largely-evaluated clustering algorithm. I don’t really see the need to rebrand it with a new name. What is the difference between GENERAL and hierarchical clustering other than the GENERAL is applied to defect prediction?}

\response{Thank you for your comment. There were indeed lack of clarity regarding the explanation of how GENERAL works, we have added more details about GENERAL\respto{XXXXXX}. The algorithm GENERAL uses hierarchical clustering to cluster projects into smaller groups based on similarity and doesn't help with actually predicting the defect. GENERAL uses the hierarchical clustering to group the projects, then bellwether method is applied at the leaf nodes of the hierarchical clustering tree to find bellwether for each leaf, then a approximation is applied and only the bellwethers are pushed up to the tree to find bellwether in upper levels. This process goes on until we find bellwether for the root node. After we have found bellwethers , we build models for predicting defect.}

\review{(3.2) Figure 1 “shows a hypothetical cost comparison in AWS between standard bellwether and GENERAL.” If the Figure is hypothetical, why do we need it? Is it based on real data? As far as I understand, the plot is merely speculation and as such is should be included in scientific papers.}

\response{Thank you for your comments. We have removed the hypothetical scenarios from sec~\ref{sec:motivation}. We have removed all the hypothetical graphs and added data from actucal experiment in this version of manuscript\respto{3-2}.}

\review{(3.3) I am also very concerned about the (unproven) assumption that we can make conclusions that hold across multiple projects. While the dataset includes 700 projects, we have no information about the project, the domain applications, critically (e.g., safety-critical systems vs. generic open-source Java libraries). I don’t really see how a model trained on dozens of open-source apache libraries can be applied to robotics, medical systems, etc. Note that for the latter domains, testing, requirements engineering, and maintenance are different and have peculiar standards (e.g., MC/CD coverage for automotive systems vs. statement coverage for non-critical systems). See below further comments about the quality of the dataset.}

\response{with respect.... but we can}

@@

\review{(3.4) Similar to Figure 1, Figure 2 discussed hypothetical results/comparisons. Why do we need to speculate on hypothetical data rather than real data? The last two paragraphs in Section 2.2 make little sense to me. There is no reason to have them, if not for contributing to the overall overselling.}

\response{Thank you for your comments. We have removed the hypothetical scenarios from sec~\ref{sec:motivation}. We have removed all the hypothetical graphs and added data from actual experiment in this version of manuscript\respto{3-2}.}

@@

\review{(3.5) Up to page 5 (Sections 1-2), the paper broadly discusses the importance of learning models from hundreds of projects to have more generic and more reliable software analytics in a broader sense. However, from Section 3 to Section 6, the manuscript focuses on defect prediction ONLY.}

\response{Thank you for your comment. In this paper, we discussed about a broader impact of learning from large number of projects to find a general conclusion. We indeed didn't emphasized on mentioning, we are using defect prediction as our case study for this paper. We have added details\respto{3-5} about using defect prediction in this paper as a case study for showing the importance of learning models from hundreds of projects.}

\review{(3.6) How can we use one single sub-domain (i.e., defect prediction) to make bold statements that should be valid for software analytics in general? This overselling concerns me a lot. This manuscript DOES NOT provide any evidence that GENERAL works and is applicable for other contexts other than defect prediction. In other words, SE is not only Defect Prediction.}

\response{Thank you for your comment. We indeed can not say that in general and can not prove external validity, but just for the projects used in this paper. which is orders of magnitude larger than anything seen before.}

% not in general. cant prove external validity. jsut for our 673 projects. wichi is orders of mangitude larger than anything seen ebfore.

\review{(3.7) Therefore, the title, the abstract, introduction, motivation, and conclusions should mention defect prediction as to the only sub-domain in which GENERAL has been evaluated. Any overselling to other domains (or software analytics in a broader sense) should be removed (perhaps mentioned as part of future work) because it is not supported by what is in the empirical study/results.}

\response{Thank you for your comment. We have changed title, the abstract, introduction, motivation, and conclusions to be more specific towards defect prediction rather than software analytics for this version.}

\review{(3.8) As mentioned in one of my comments above, the script seeks to model generalizability looking at the number of projects (and size) as solely dimension to look at. But what about the quality attributes, such as the application domain? What are the application domains of the projects? Are there only open-source projects? How about industrial projects, including the financial, automotive, and robotics sectors? How many web and mobile applications are in the sample? Does the dataset cover these domains? If not, how can we claim that 700 projects can bring us to generalizability?}

\response{not in general. cant prove external validity. just for our 673 projects. which is orders of magnitude larger than anything seen before.XXXX}

\review{(3.9) Furthermore, the dataset looks quite strange to me. Looking at the defect distributions (left-most boxplot in Figure 4), I do see that 75\% of the projects (the last quartile) have more than 60\% of defective modules (classes/methods?). Some have a defective percentage above 80\%. Do we need machine learning to predict defects in projects where almost all modules are defectives? In these projects, a simple, constant classifier would work the best. The results also show this for ZeroR in Section 5.}

\response{unclear on this. zeroR tells us that it is not enough to do simple things. Not sure how to answer.XXXX}

@@

\review{(3.10) Throughout the manuscript, the complexity of GENERAL is suggested to be $O(m * (N/m)^2)$. But there is proof about the complexity whatsoever. Either the manuscript cites proofs from existing papers (e.g., related work on hierarchical clustering) or provides a complete proof (perhaps in an appendix).}

\response{Thank you for your comment, we didn't included detailed analysis of complexity of our method in the last manuscript. We have added much details and an step by step analysis\respto{3-10} of complexity of the algorithm shown in Fig~\ref{fig:Pseudo-code}.}

\review{(3.11a) All the results are summarized in one single table (Figure 7), which shows the mean and the standard deviation of five evaluation metrics, as well as the rank of the statistical tests. There are two problems in aggregating the data in this way: (1)I am not sure that the arithmetic mean and the standard deviation are the appropriate metrics to use. Are the data normally distributed? Do we have many outliers? Perhaps, median and IQR are more appropriate as they are less affected by outliers.}

\response{Thank you for your comment, you are quite correct. We used arithmetic mean and standard deviation as our metrics to showcase our result in the last manuscript, which may be affected by outliers and skew the results. In this manuscript, we have replaced arithmetic mean and standard deviation with median and IQR in figure~\ref{fig:Statistical}.}

\review{(3.11b)Maybe, the boxplots would be the most appropriate way to show the distributions. (2)The average across 700 projects makes little sense and hides what happens in each project. What happens per project? In how many projects does GENERAL performs better than the standard bellwether learner?}

\response{Thank you for your comments. The Fig~\ref{fig:Statistical} is a form of boxplot, where the black dot represents the median and the spread of the black line represents the 25th and 75th percentile of the data. Alternatively we can include all the results instead of just showing the median and IQR, but it will occupy too much space.}

\review{(3.12) Section 5 contains the following recommendation “As to ZeroR, we cannot recommend that approach. While ZeroR makes few mistakes (low ifas and low pfs), it scores badly on other measures (very low recalls and popt(20).” This argument does not convince me as ZeroR gets the best results for two metrics (as far as I understand). Please elaborate more on why we cannot use ZeroR. Besides, ZeroR may work relatively well because of projects with a very large number of defects. Perhaps, some in-depth analysis of the correlation between defect distributions and performances of the models would be very useful.}

\response{Thank you for your comments, in the last manuscript we did not properly explained why the model ZeroR can not be recommend. We have updated the figure~\ref{fig:Statistical} to replace arithmetic mean and standard deviation with median and IQR. We can see from the figure~\ref{fig:Statistical}, the ZeroR model has a recall and pf of zero with IQR diff between 75th and 25th percentile as 100, which signifies as the model either predicts everything as defective or non-defective it will not be able to predict any defective module at all if the defect ratio is less than 50\%, while for projects with defect ratio is more than 50\% it will predict everything as defective with high false positive.XXXX}

\review{(3.13) Section 5 (RQ3) ends with two recommendations about critical and non-critical systems. However, I could not find any analysis that can support these recommendations. I also queried the paper looking for the keywords “critical systems,” but I could not find anything except the recommendation with these keywords. To address this, there are only two mutually exclusive solutions: either remove the recommendations or add in-depth analysis that can provide empirical evidence to the claims.}

\response{Thank you for your valuable comments, the text for section~\ref{sec:rq6} was indeed confusing, we have made appropriate changes to better explain our analysis of a general defect prediction model learned by analyzing 627 projects. We have also removed any ambiguous keyword which might not be appropriate in this context. The changes has been added in \respto{3-13}.}
